Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\section{Related Works}
This section will discuss two related works that inspired this paper.

>>>>

\section{Related Works}
This section will discuss two related works in the field of performance regression.

\subsection{Performance Regression Detection in DevOps}
This study \cite{regression-detection} proposes to perform regression detection
performance at the DevOps stage, i.e. at the level of the intended source code change
the main thing is to avoid detecting performance regressions after the app is deployed
and running in a production environment. There are two ways proposed by the research
This is to detect performance regressions at the DevOps stage, namely:

\subsection{A Real-time Trace-level Root-cause Diagnosis System in Alibaba Datacenters}
